---
title: "Quarto Customization Practice"
author: "Henry Oliver"
format: html
execute: 
  warning: false
---

Suppressing warning and messages JUST for this code chunk

```{r}
#| warning: false
#| message: false
library(tidyverse)

```

Running code but not showing code OR output
```{r}
#| include: false
# return first 6 lines of starwars data
head(starwars)

#return dimensions of starwars table
dim(starwars)
```

Showing output, but not code.
```{r}
#| warning: false
#| echo: false

ggplot(data = starwars, aes(x = height, y = mass, color = mass)) + 
  geom_point() +
  labs (x = "Height in cm", y = "Mass in Kg")


```

Show only code and output
```{r}
#| warning: false
#| fig-cap: "caption text"
#| fig-alt: "figure alt text"
ggplot(data = starwars, aes(x = height)) +
  geom_histogram(color = "purple", fill = "gold")

```

Find summary stats for Star Wars characters
```{r}
#| echo: false
sw_height_mean <- mean(starwars$height, na.rm = TRUE)

sw_height_median <- median(starwars$height, na.rm = TRUE)

sw_height_var <- var(starwars$height, na.rm = TRUE)

sw_height_sd <- sd(starwars$height, na.rm = TRUE)

```

The mean height of the characters in Star Wars is `r round(sw_height_mean, 3)`.

The median height of the characters in Star Wars is `r sw_height_median`.

The variance of height of characters in Star Wars is `r round (sw_height_var, 2)`.

